Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-11-13 manuscript/manuscript.tex
BH's suggestion

We demonstrate how to apply TICA, suggest how to interpret the projected coordinates and compare the results to other dimension reduction techniques in Notebook (02).

>>>>

We demonstrate how to apply TICA, suggest how to interpret the projected coordinates, and compare the results to other dimension reduction techniques in Notebook (02).
